Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-04 ms.tex
more updates to long dark section.

The long dark frames used for detector characterization are 108 groups of 1 frame each read out if full frame mode and are 10.7 sec in duration for one long integration making up one exposure.
These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
In the raw data, there are 4 prominent vertical stripes due to offsets in the read-out amplifiers.
Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.

@@

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top Left:} The time series constructed from raw dark frames.
{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied. 
{\it Bottom Left:} An example read pair subtraction with an overlay of the apertures.
{\it Bottom Right:} AN example read pair subtraction after reduction steps with an overlay of the apertures.
\textcolor{red}{To Do: redo the time series without normalization since we want to show DN.}}\label{fig:longDarkPhot}
\end{figure*}

\textcolor{red}{To do}
\begin{itemize}
	\item Make the two apertures have the same Y value
	\item Make the two apertures have the same 
	\item Put in a third aperture above the source
	\item Re-label the aperture from "src" to 0
	\item Use more pixels to reduce the 1/f noise (say median of another amplifier along the X direction)
\end{itemize}

>>>>

The standard long dark exposures used for detector characterization are a single integration that is 108 groups of 1 frame each (so-called RAPID mode).
The detectors are read in full frame mode so that each frame is 10.7 sec in duration with 4 output amplifiers in use.
These long dark integrations are broken into 54 sequential pairs of images that are subtracted from each other (integration 1 minus integration 0, 3 minus 2, 5 minus 4 etc. in a zero-based counting scheme).
Figure \ref{fig:longDarkPhot} shows an example dark read pair from the integration (frame 55 minus frame 54).
In the raw data, there are 4 prominent vertical stripes due to offsets in the read-out amplifiers.
Additionally, there obvious correlations along the fast-read direction (horizontally) due to 1/f noise.

@@

In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
If uncorrected, this extra read noise will contribution 7000 ppm to the time series!
As can be seen in Figure \ref{fig:longDarkPhot}, there a significant correlations along the fast read (X) direction of the detector due to 1/f noise.
These can be reduced with the side reference pixels as well as a median of the entire image along the X direction.
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{ap_labels_dark_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{ap_labels_darkRed_NRCALONG-DARK-7235074213_1.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Raw.pdf}
\includegraphics[width=.49\columnwidth]{long_dark_Reduced.pdf}
\caption{Time series of a 70 pixel radius photometric aperture obtained during a long dark exposure for detector ALONG=A5. The long dark exposure of 108 frames is used to construct 54 pairs of reads that are subtracted, in analogy with a series of integrations.
{\it Top Left:} An example read pair subtraction with an overlay of the apertures.
{\it Top Right:} An example read pair subtraction after reduction steps with an overlay of the apertures.
{\it Top Left:} The time series constructed from raw dark frames.
{\it Top Right:} The time series with gain, bias, reference, non-linearity and IPC correction applied. 
}\label{fig:longDarkPhot}
\end{figure*}

\textcolor{red}{To do}
\begin{itemize}
	\item Confirm that the side reference pixels are most critical in reducing the noise
\end{itemize}
